PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-20 paper/ms.tex
typo
fix typo

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{Two Stars, Two Signals, No Planet}

@@

\begin{abstract}
  PTFO$\,$8-8695 (CVSO\,30) is a star in the 7--10 million year old
  Orion-OB1a cluster that shows brightness dips that resemble
  planetary transits.  Although strong evidence against the planet
  hypothesis has been presented, the possibility remains debated in
  the literature.  To obtain further clues, we inspected data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS) and the ESA
  Gaia mission.  The Gaia data suggest that PTFO$\,$8-8695 is a
  binary: the photometric data show it to be overluminous with respect
  to members of its kinematic group, and the astrometric data are
  inconsistent with a single star.  The TESS light curve shows two
  different photometric periods. The variability is dominated by a
  sinusoidal signal with a period of 11.98$\,$hr, presumably caused by
  stellar rotation.  Also present is a 10.76$\,$hr signal consisting
  of a not-quite sinusoid interrupted by hour-long dips, the type of
  signal previously intepreted as planetary transits.  The phase of
  the dips is nearly 180$^\circ$ away from the phase of the originally
  reported dips. As noted previously, this makes them difficult to
  explain as planetary transits.  Instead, we believe that
  PTFO$\,$8-8695 is a pair of young and rapidly rotating M dwarfs, one
  of which shows the same ``transient-dipper'' behavior that has been
  seen in at least 5 other cases.  The origin of these transient dips
  is still unknown but likely involves circumstellar material.
\end{abstract}

@@

Radial velocity (RV) measurements over sufficiently long timescales
could also reveal the presence of multiple stars in this system.
Unfortunately, the available RV data for \ptfo\ is sparse, presumably
due to the difficulties of performing RV observations of such a faint
and rapidly rotating star.  The RV datasets with the longest time
baselines we could find in the literature were those reported by
\citet{van_eyken_ptf_2012}.  These included 5 Keck/HIRES measurements
acquired over 10 days in April 2011, and 4 HET/HRS measurements
acquired over 10 days in February 2011.  The root-mean-squared RV over
each 10-day span was $\approx$$2\,{\rm km}\,{\rm s}^{-1}$, consistent
with the measurement precision.  Although \citet{van_eyken_ptf_2012}
tried a CCF-based RV reduction technique, they eventually found that
manually selecting absorption lines and measuring line centroids was
more effective.  While \citet{yu_tests_2015} acquired 22 further
Keck/HIRES spectra over one night in December 2013, those points were
not reduced to velocities Further radial-velocity observations could
potentially confirm or refute the presence of binary companions.

@@

analysis of the Gaia data provide independent support for the

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{May 15, 2020}
\revised{\today}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{Two Stars, Two Signals, No Planet}

@@

\begin{abstract}
  PTFO$\,$8-8695 (CVSO\,30) is a star in the 7--10 million year old
  Orion-OB1a cluster that shows brightness dips that resemble
  planetary transits.  Although strong evidence against the planet
  hypothesis has been presented, the possibility remains debated in
  the literature.  To obtain further clues, we inspected data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS) and the ESA
  Gaia mission.  The Gaia data suggest that PTFO$\,$8-8695 is a
  binary: the photometric data show it to be overluminous with respect
  to members of its kinematic group, and the astrometric data are
  inconsistent with a single star.  The TESS light curve shows two
  different photometric periods. The variability is dominated by a
  sinusoidal signal with a period of 11.98$\,$hr, presumably caused by
  stellar rotation.  Also present is a 10.76$\,$hr signal consisting
  of a not-quite sinusoid interrupted by hour-long dips, the type of
  signal previously interpreted as planetary transits.  The phase of
  the dips is nearly 180$^\circ$ away from the phase of the originally
  reported dips. As noted previously, this makes them difficult to
  explain as planetary transits.  Instead, we believe that
  PTFO$\,$8-8695 is a pair of young and rapidly rotating M dwarfs, one
  of which shows the same ``transient-dipper'' behavior that has been
  seen in at least 5 other cases.  The origin of these transient dips
  is still unknown but likely involves circumstellar material.
\end{abstract}

@@

Radial velocity (RV) measurements over sufficiently long timescales
could also reveal the presence of multiple stars in this system.
Unfortunately, the available RV data for \ptfo\ is sparse, presumably
due to the difficulties of performing RV observations of such a faint
and rapidly rotating star.  The RV datasets with the longest time
baselines we could find in the literature were those reported by
\citet{van_eyken_ptf_2012}.  These included 5 Keck/HIRES measurements
acquired over 10 days in April 2011, and 4 HET/HRS measurements
acquired over 10 days in February 2011.  The root-mean-squared RV over
each 10-day span was $\approx$$2\,{\rm km}\,{\rm s}^{-1}$, consistent
with the measurement precision.  Although \citet{van_eyken_ptf_2012}
tried a CCF-based RV reduction technique, they eventually found that
manually selecting absorption lines and measuring line centroids was
more effective.  While \citet{yu_tests_2015} acquired 22 further
Keck/HIRES spectra over one night in December 2013, those points were
not reduced to velocities. Further radial-velocity observations could
potentially confirm or refute the presence of binary companions.

@@

analysis of the Gaia data provides independent support for the
